%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}
%\usepackage{hyperref}

% moderncv themes
\moderncvtheme[green]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Chris}
\familyname{Stucchio}
%\title{Resumé title (optional)}               % optional, remove the line if not wanted
%\address{170 W 74th St, Apt 1212}{NY, NY 10023}    % optional, remove the line if not wanted
%\mobile{646.926.7840}
\email{stucchio@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{https://github.com/stucchio}
 % optional, remove the line if not wanted
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"They can kill you, but the legalities of eating you are quite a bit dicier" - David Foster Wallace}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Profile}
I'm a hands on data science leader, building teams and that generate automated decisions and insights into what is unknown. I build robust, efficient software systems that degrade gracefully when things don't go as planned. For details see my github (\link{https://github.com/stucchio}) or blog (\link{http://www.chrisstucchio.com/blog/index.html}).

\section{Experience}
\cventry{2017-Present}{GetSimpl Technologies}{Consultant}{Bangalore, India}{}{
  Simpl is a mobile-first lending startup, build on underwriting loans based on alternative data sources (most of Asia lacks formal credit infrastructure). At Simpl I've been leading the effort to build out a reliable, scalable automated underwriting system. Specific goals include reliably predicting defaults and assessing credit limits, risk controls, balancing risk against the need for growth, as well as using data to help guide business decisions.
\newline
- Major focus includes implementing engineering best practices, simplifying legacy systems, and standardizing the software stack.
\newline
- Standardizing and assessing key metrics for the company and accurately measuring them.
}

\cventry{2015-2017}{Wingify (VWO/Pushcrew)}{Director of Data Science}{USA, India}{}{
  Led a team of 6 data scientists and engineers, focused on data science and highly performance infrastructure. Communicated and evangelized the importance of statistics to customers and prospects.
\newline
- I designed and architected SmartStats, VWO's new Bayesian A/B testing engine. Prior to SmartStats, A/B testing on the web was broken. The statistics were often calculated incorrectly and virtually always misinterpreted. SmartStats adjusts the statistics to match the way humans use them and fixes these problems.
\newline
- Built a behavioral targeting system for push notifications and site modifications.
\newline
- Used statistical techniques to improve delivery and click through rates of push notifications, giving PushCrew the highest delivery rates in the industry.
\newline
- Served as acting Engineering Manager of PushCrew (9 months), focusing on implementing engineering hygiene and best practices.
}
\cventry{2014-2015}{Wingify/VWO}{Consultant}{USA, India}{}{}
\cventry{2013-2015}{Independent Consultant}{}{USA, UK, India}{}{
Consultant for a variety of clients in the legal, financial and e-commerce spaces. More significant projects include:
\newline
- Forensic accounting, analyzing equity and options trades in search of criminal activity. Modeling price impact and regulatory compliance.
\newline
- Analysis and implementation of microfoundation-based macroeconomic models in order to perform macroeconomic modelling beyond the regime of historical data.
\newline
- Design and analysis of Bayesian algorithms for improving product discovery on certain fashion sites.
}

\cventry{2012-2013}{Patch}{Senior Software Engineer}{NY, NY}{}{
I taught Patch how to use data to make decisions. I built an A/B testing framework and pushed testing and data to the forefront of Patch engineering culture - all major decisions are now driven by A/B tests. I was also the primary architect on Chilaquiles, the realtime monitoring and recommendation system that powers Patch's content selection. Primary technologies used were Scala, Akka and Hadoop.
\newline
- Designed realtime Bayesian recommendation system, generating an 120\% increase in Click Through Rate and increasing page views by 2\%.
\newline
- Built behavioral spam filtering system which blocked spammers based on site behavior.
\newline
- Built funnel tracking system, discovering numerous bottlenecks in the creation of User Generated Content.
\newline
- Assorted backend infrastructure work - SQL query optimization and schema design, performance optimization, etc. Made the site hundreds of milliseconds faster and the codebase cleaner.
\newline
}

\cventry{2011-2012}{Styloot}{CTO}{NY, NY and Pune, India}{}{
Designed and built \href{http://styloot.com}{Styloot}, a visual search engine for women's fashion. Users can create the visual representation with Styloot's create page or they can upload photographs with Styloot's iPhone app, and Styloot will find items of similar appearance in our catalog. Managed a technology team of 3 people and an oracle staff of 8.
\newline
- Designed a NoSQL in-memory data indexer (called Hobo) to handle search.
\newline
- Performed experiments on women's perception to determine what features are important in fashion search.
\newline
- Technologies used: Python/Django, C++, Java and Hadoop (all hosted on AWS). We also use a team of human oracles as an in-house version of Mechanical Turk.
}

\cventry{2010-2011}{Mesh Capital}{Quantitative Trader}{Jersey City, NJ}{}{
Devised and implemented strategies for high frequency trading. Designed a global predictive strategy using activity in high volume stocks to predict price movements of low volume stocks. Micro-optimized various system components to reduce latency during high volume periods. Devised dynamic portfolio rebalancing strategy to reduce risk and increase profits. All work done in Java.
}
\cventry{2009-2010}{Trading Games}{Quantitative Developer (Consultant)}{NY, NY}{}{
Designed and implemented alpha version of a prediction market platform for an early stage startup. Platform consists of a backend which acts as an exchange for binary event futures, a frontend which is a web-based user interface allowing users to buy and sell event futures, and a JSON API which allows external developers to interface with the system.
\newline
- Technologies used: Python/Django, C++, AMQP (RabbitMQ)
}
\cventry{2007-2010}{Courant Institute, NYU}{Postdoctoral Scholar}{NY, NY}{}{
Developed a model-based reconstruction algorithm for MRI (Magnetic Resonance Imaging) as well as a supporting library of computational geometry algorithms. This involves both image processing and computational geometry. Developed new numerical algorithms for solving wave equations (particularly electromagnetism and superfluids) and built a model of quantum decoherence to help understand the measurement problem.
}
\cventry{2002-2007}{Rutgers University}{Bevier Graduate Fellow}{Piscataway, NJ}{}{
Developed a software package for solving the partial differential equations involved in modeling nanoscale quantum transport (written in Python and C). Managed a team of two undergraduate researchers for part of the project. In collaboration with experimentalists at the Technion/Israel Institute of Technology, I used the aforementioned software package to model optics experiments. I also taught courses ranging from Precalculus to Differential Equations.
}

\section{Skills}
\cventry{}{Analytical Skills}{}{Experience in high frequency trading, image processing, theoretical physics and machine learning}{}{}
\cventry{}{Languages}{}{Python, Scala, Java, C++, Haskell, Javascript, Emacs Lisp}{}{}

\section{Education}
\cventry{2007--2010}{New York University}{Postdoctoral Scholar, Mathematics}{}{NY, NY}{}
\cventry{2002-2008}{Rutgers University}{Ph.D., Mathematics}{}{Piscataway, NJ}{}
\cventry{2000-2002}{Stevens Institute of Technology}{B.S. Mathematics and Physics}{}{Hoboken, NJ}{}

% PUBLICATIONS
\nocite{us:waveCollapsedoesntMatter, us:TDPSFjcp, us:TDPSFrigorous, us:multiscale, us:anisotropic, us:solitongun, us:dipoledelta, us:ionizationPRL, us:dirichleterrorbound, barak:153901, meleslie:wavefrontPaper, meleslie:curveppaer}

\bibliographystyle{abbrv}
\bibliography{/home/stucchio/Documents/my_papers/stucchio}

\cventry{}{Author of \url{www.chrisstucchio.com}, a widely read blog.}{}{}{}{Referenced by the Huffington Post, National Review, Reuters, Business Insider, and MarginalRevolution.com (among others).}{ }

\section{Talks (Selected)}
\cventry{2015}{Conversion Hotel}{Bayesian A/B Testing}{}{Texel, Netherlands}{}{}
\cventry{2015}{Crunch Conf}{Multiple Comparisons: Make Your Boss Happy with False Positives}{}{Budapest, Hungary}{}{}
\cventry{2014}{Pune Scala Symposium}{Number Crunching in Scala}{}{Pune, India}{}{}
\cventry{2012}{VIT Computer Science Seminar}{}{}{Pune, India}{}{}
\cventry{2009}{Rutgers University Mathematical Physics Seminar}{}{}{Piscataway, NJ}{}{}
\cventry{2008}{Wolfgang Pauli Institute}{}{}{Vienna, Austria}{}{}
\cventry{2008}{SIAM Annual Meeting}{}{}{San Diego, CA}{}{}
\cventry{2008}{Frontiers in Applied and Computational Mathematics}{}{}{Newark, NJ}{}{}
\cventry{2007}{University of Chicago Applied Mathematics Seminar}{}{}{Chicago, IL}{}{}
\cventry{2007}{SIAM Conference on Dynamical Systems}{}{}{Snowbird, UT}{}{}
\cventry{2007}{Princeton Mathematical Physics Seminar}{}{}{Princeton, NJ}{}{}

\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

% Publications from a BibTeX file


\end{document}


%% end of file `template_en.tex'.
